---
title: "Visualizing Linear Regression Models"
author: "Felix Schneider"
date: "8/14/2020"
output: 
  slidy_presentation: 
    incremental: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

## The Idea for the App
- In the *Regression Models* Course, we learned that the coefficients of a linear model for the outcome on a particular regressor depend on whether other regressors are present in the model formula.
- This App provides the ability
  * to compose the regression formula by checking the desired regressors in a checkbox group,
  * view the resulting formula,
  * view the coefficients of the associated linear model,
  * and compare the resulting regression line with a smoother line which takes only the plotted regressor into account.
- Various regressors can be selected for the x-axis of the plot.
- The data that the App works with come from a data set in the R `datasets` packages, and is called `swiss`.

## Programming Challenges
There are two locations in the code that posed a challenge during programming in the `server.R`.

The aesthetics mapping in the `ggplot` command
```{r eval=FALSE, echo=TRUE}
pr <- input$plotRegressor
g <- ggplot(swiss, aes(.data[[pr]], Fertility))
```

The aesthetics mapping in the `geom_abline` command
```{r eval=FALSE, echo=TRUE}
pr <- input$plotRegressor
g + geom_abline(slope=model()$coef[{{pr}},"Estimate"],
               intercept=model()$coef["(Intercept)","Estimate"],
               color="red",size=1)
```


## Tidy Evaluation, *Env*-Variables and *Data*-Variables
- The term *variable* has two different meanings when programming in R.
  a) an **object** that is created with the `<-` operator that contains variable contents. These are so called **env**-variables since they are "defined" in an environment.
  b) a **column** in a data frame that is usually referred to with the `$` character (`dataframe$variable`). These are so called **data**-variables since they are "defined" by the data.
- The `aes()` command requires a *data*-variable, but the code wants to provide that in an *env*-variable. This is solved with the `.data[[<variable>]]` construct.
- The `geom_abline()` command requires the value of an *env*-variable in a function call parameter. This is solved with the `{{<variable>}}` construct.

## Publish the App to shinyapps.io
The following code is executed during the knit process and reproducibly deploys the App to shinyapps.io.
```{r deploy_app, echo=TRUE, comment="", cache=TRUE}
library(rsconnect)
deployApp("CourseProjectApp/")
```



